Self Regulation Ontology Retest Data Report

### 2018-01-25 code/SRO_Report.Rmd
updating report with new releases

```{r}
hddm_refits <- read.csv(paste0('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')

@@

test_data = cbind(test_data$sub_id, test_data[,names(test_data) %in% names(hddm_refits) == FALSE])

names(test_data)[which(names(test_data) == 'test_data$sub_id')] <-'sub_id'

test_data = merge(test_data, hddm_refits, by="sub_id")
```

@@

```{r message=FALSE, warning=FALSE}
boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/bootstrap_merged.csv')

@@

```{r echo=FALSE}
measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)
```

>>>>

```{r}
hddm_refits <- read.csv(paste0(retest_data_path,'t1_data/hddm_refits_exhaustive.csv'))

@@

#drop hddm columns from test_data
test_data = cbind(test_data$sub_id, test_data[,names(test_data) %in% names(hddm_refits) == FALSE])

#fix naming before merging
names(test_data)[which(names(test_data) == 'test_data$sub_id')] <-'sub_id'

#merge hddm refits to test data
test_data = merge(test_data, hddm_refits, by="sub_id")
```

@@

```{r message=FALSE, warning=FALSE}
boot_df <- read.csv(gzfile(paste0(retest_data_path,'bootstrap_merged.csv.gz')))

@@

```{r echo=FALSE}
measure_labels <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/measure_labels.csv')
measure_labels = measure_labels %>% select(-measure_description,-measure_type,-measure_type_Ian,-measure_type_Russ,-notes,-Patrick_hates)

# retest_report_vars[(retest_report_vars %in% measure_labels$dv == FALSE)]
# measure_labels$dv[(measure_labels$dv %in% retest_report_vars == FALSE)]
```
